---
title: "CV"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Curriculum Vitae || Ferris S. Tucker
(myp) hon - enu - mber | myemail @ domain.com

***
> stuff about me

###**Previous Experience** |

*   I would put a job here ( **DATE** )

    * *kinds, of, tasks*

    * *list, of, skills*
    
###**Education** |

*   School #1 ( **DATE - CHRONOLOGICAL Z-A** )

    * *studied, stuff*

    * *any awards*
    
*   School #2 ( **DATE - CHRONOLOGICAL Z-A** )

    * *studied, stuff*

    * *any awards*
```{r chunk-name}
## number 27.4.2
```

```{r raw_data}
rawdata <- readr::read_csv("a_very_large_file.csv")
```

```{r processed_data, cache = TRUE, dependson = "raw_data"}
processed_data <- rawdata %>% 
  filter(!is.na(import_var)) %>% 
  mutate(new_variable = complicated_transformation(x, y, z))
```

#27.6.1 // ran with error on purpose
---
output: html_document
params:
  my_class: "suv"
---

```{r setup, include = FALSE}
library(ggplot2)
library(dplyr)

class <- mpg %>% filter(class == params$my_class)
```

# Fuel economy for `r params$my_class`s

```{r, message = FALSE}
ggplot(class, aes(displ, hwy)) + 
  geom_point() + 
  geom_smooth(se = FALSE)
```
